---
title: "Tokopedia"
author: "Nathasya Pramudita"
date: "2023-11-20"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r call the packages, message=FALSE, warning=FALSE}
library(tidyr) # for tidying data
library(dplyr) # for manipulating data
library(readr) # reading the df
library(forcats) # manipulating factor data type
library(ggplot2) # for visualization
library(extrafont) # for changing the font in viz
```

# Tokopedia Study Case
## Summary of the dataset

- There's 11 variables and 5400 observant, with 33 unique data in `category` variables (meaning this data only focus on 33 product only),
- They didn't have range of time on when the data is obtain.
- Location in this data is focus on Java island (with exception in Denpasar, Palembang, and Medan).
- Overall rating that customer gives are range from `4.1` to `5.0` (they never give the supplier <4).
- The `emotion` ordinal data type is consist of `Anger`, `Fear`, `Happy`, `Love`, and `Sadness`.

*disclaimer: the data that I used is obtain from (mendeley dataset open source) [https://data.mendeley.com/datasets/574v66hf2v/1]. This dataset is collection of Indonesian product review data annotated with emotion and sentiment labels. The data were collected from one of the giant e-commerce in Indonesia named Tokopedia. The dataset contains product reviews from 29 product categories on Tokopedia that use the Indonesian language. Each product review is annotated with a single emotion, i.e., love, happiness, anger, fear, or sadness. The group of annotators does the annotation process to provide emotion labels by following the emotions annotation criteria created by an expert in clinical psychology. Other attributes related to the product review are also extracted, such as Location, Price, Overall Rating, Number Sold, Total Review, and Customer Rating*


```{r import dataset, message = F}
tokopedia <- read_csv("~/Datasets/Tokopedia dataset/PRDECT-ID Dataset.csv") %>% 
  rename_all(tolower) %>% 
  mutate(`overall rating` = as.factor(`overall rating`),
         `customer rating` = as.factor(`customer rating`),
         sentiment = as.factor(sentiment),
         emotion = as.factor(emotion))
tokopedia %>% head(5)
```


```{r wrangling dataset, message = FALSE}
# created diff df for analysis process
# customer rating
customer_rating <- tokopedia %>%
  group_by(category, `customer rating`) %>% 
  summarize(`total price` = sum(price),
         `total review` = sum(`total review`)) %>%
  select(category, `customer rating`, `total price`, `total review`) %>% 
  arrange(category, `customer rating`)
# emotion rating
emotion_rating <- tokopedia %>% 
  group_by(category, emotion) %>%
  summarize(`total price` = sum(price),
         `total review` = sum(`total review`),
         `total sold` = sum(`number sold`)) %>% 
  select(category, emotion, `total price`, `total review`, `total sold`) %>% 
  arrange(category, emotion, `total price`)
# total sold of product based on categories
most_purchase <- tokopedia %>% 
  group_by(category) %>% 
  summarize(`total price` = sum(price),
            `total sold` = sum(`number sold`)) %>% 
  select(category, `total price`, `total sold`) %>% 
  arrange(desc(`total price`))
```


```{r created font and label for the viz, eval=FALSE, include=FALSE}
# create font for label and graph (I am not using this)
font_style <- list(family = "Vivaldi",
                   size = 10,
                   color = "black")
label <- list(bgcolor = "#eeeeee",
              bordercolor = "transparent",
              font = font_style)
```


```{r create Top-7 best purchase product in Tokopedia}
# create Top-7 best purchase product in Tokopedia
most_purchase %>%
  mutate(price_in_million = round(`total price`/1000000),
         category = fct_reorder(category, price_in_million)) %>% 
  head(7) %>%
  ggplot(aes(category, price_in_million, fill = category))+
  geom_col(alpha = .7, width = 0.5, show.legend = FALSE) +
  coord_flip()+
  labs(title = "Most Purchasing Product on Tokopedia",
       x = "",
       y = "Price in Million Rupiah")+
  scale_fill_brewer(palette = "Set2")+
  theme_light() +
  theme(text = element_text(family = "Segoe UI Light"))
```


```{r created graph based on emotion rating}
# created graph based on emotion rating
emotion_rating %>% 
  mutate(price_in_million = `total price`/1000000,
         emotion = fct_reorder(emotion, price_in_million)) %>% 
  filter(category %in% c("Phones and Tablets", "Tour and Travel",
                         "Precious Metal", "Electronics")) %>% 
  ggplot(aes(emotion, price_in_million, fill = emotion))+
    geom_col(alpha = .7, width = .5, show.legend = F) +
    coord_flip() +
    facet_wrap(~category) +
    labs(title = "Top-4 Most Purchase Product Based on Emotion Ranking",
         x = "",
         y = "Price in Million Rupiah") +
    scale_fill_manual(breaks = c("Sadness", "Love", "Happy", "Fear", "Anger"),
                     values = c("#F7D060", "#FD8A8A", "#BAFFB4", "#F39472", "#FF4848"))+
  theme_classic() +
  theme(text = element_text(family = "Segoe UI Light"))
```


```{r product with the higher negative emotion rating}
emotion_rating %>% 
  filter(emotion %in% c("Fear", "Sadness", "Anger"),
         category %in% c("Animal Care", "Automotive", "Beauty", "Body Care")) %>% 
  group_by(category, emotion) %>% 
  summarize(`total review` = sum(`total review`)) %>% 
  mutate(emotion = fct_reorder(emotion, `total review`),
         `total review` = `total review`/1000) %>% 
  arrange(`total review`) %>% 
  ggplot(aes(emotion, `total review`, fill = emotion)) +
    geom_col(alpha = .7, width = .5, show.legend = F) +
    coord_flip() +
    facet_wrap(~category) +
    labs(title = "Top-4 Product With the Higher Negative Emotion Review",
         x = "",
         y = "Total Review in Thousand") +
    scale_fill_manual(breaks = c("Sadness", "Fear", "Anger"),
                      values = c("#f7d060", "#F39472", "#ff4848")) +
    theme_classic() +
    theme(text = element_text(family = "Segoe UI Light"))
```



```{r created graph based on customer rating star}
# created graph based on customer rating star
customer_rating %>% 
  mutate(price_in_million = `total price`/1000000) %>% 
  filter(category %in% c("Phones and Tablets", "Tour and Travel",
                         "Precious Metal", "Electronics")) %>% 
  ggplot(aes(`customer rating`, price_in_million, fill = `customer rating`))+
  geom_col(alpha = .7, linewidth = .5, show.legend = F) +
  facet_wrap(~category) +
  labs(title = "Top-4 Most Purchase Product Based on Customer Rating",
       x = "",
       y = "Price in Million Rupiah") +
  scale_fill_brewer(palette = "YlOrBr") +
  theme_classic() +
  theme(text = element_text(family = "Segoe UI Light"))

```


```{r treemap graph, eval=FALSE, include=FALSE}
library(treemap)
# create treemap for the same dataset
treemap(most_purchase,
        index = "category",
        vSize = "total_price",
        type = "index",
        title = "The most purchasing product on Tokopedia")
# tried to see some correlation
tokopedia %>%
  filter(price < 250000) %>% 
  slice(1:10) %>% 
  ggplot(aes(number.sold, price, color = category)) +
  geom_point() +
  theme(legend.position = "none")
```

```{r corelation between negative and positive emotion, message=FALSE}
tokopedia %>% 
  group_by(emotion, sentiment) %>% 
  summarize(sum = sum(`number sold`)) %>% 
  mutate(emotion = fct_reorder(emotion, sum),
         sum = round(sum/1000)) %>% 
  ggplot(aes(emotion, sum, fill = sentiment)) +
  geom_col(linewidth = 1.5) +
  labs(x = "",
       y = "Total Product Sold",
       title = "Total Sold Product Based on Emotion and Sentiment Rating"
       ) +
  geom_text(aes(label = sum), vjust = 1) +
  theme_classic() + 
  theme(text = element_text(family = "Segoe UI Light"),
        legend.position = "bottom") +
  scale_fill_manual (values = c("#af2655", "#b4bdbf"))
```

```{r overall rating of all product}
# overall rating of all product in Tokopedia ds
tokopedia %>% 
  mutate(`overall rating` = as.numeric(`overall rating`)) %>% 
  ggplot(aes(`overall rating`)) +
  geom_histogram(binwidth = 4, fill = "#ead123") +
  labs(title = "Customers rating of all product in Tokopedia") +
  theme_classic() +
  theme(text = element_text(family = "Segoe UI Light"))
```

---
## Finding

From the analysis above, what we find is:

- Product that worth the most are `Phone and tablet`, `Tour and travel`, `Precious metal`, `Electronic` and `Gaming`.
- The best product that get positive emotion are `Phone and tablet`, while `Precious metal` and `Tour and travel` are side by side, while `Electronic` is in the last position. We need to analyze more deeply why this phenomena occur.
- While product that get the higher negative rating is `Body Care` and `Animal Care` (negative emotion consist of `Sadness`, `Anger`, and `Fear`).
- `Precious metal` and `Tour and Travel` usually get 5 stars rating.
- `Sadness` are the most frequent emotion that customers choose after receive the product.
- And frequent rating that customers pick for overall product are (higher percentage) 7.5 to 10